Do More Polling Locations in Wards Increase Turnout? An Analysis of the 2022 Toronto Municipal Election

### 2023-05-30 outputs/paper/paper.qmd
Set up work space and loaded tidyverse package. Began writing code to read in the cleaned voter statistics and voting locations data sets.
Updating file names for the code to read in the cleaned data sets.
Adjusting the script to read in the two cleaned data sets
Removed existing code to read in cleaned data because it had errors
Added "here" package to help read in the cleaned data. Wrote code to read in the cleaned voter statistics and voting locations data sets.

```{r}

```

>>>>

```{r}
#| message: false
#| echo: false

#### Workspace set-up ####

## Load packages
library(tidyverse)
library(knitr)
library(here)

#read in cleaned data #
cleaned_voter_statistics <- read.csv(here::here("inputs/data/cleaned_voter_statistics.csv"))
show_col_types = FALSE

cleaned_voting_locations <- read.csv(here::here("inputs/data/cleaned_voting_locations.csv"))
show_col_types = FALSE
```

## Introduction
